### 2009-04-10 docs/runtime_parameters/runtime_parameters.tex
more descriptions

\verb=  dpdt_factor =  &   &  0.0d0 \\
\verb=  drdxfac =  &   &  1 \\

@@

\verb=  evolve_base_state =  &   &  .true. \\

@@

\verb=  grav_const =  &   &  -1.5d10 \\

@@

\verb=  init_shrink =  &   &  1.0 \\

>>>>

\verb=  dpdt_factor =  & factor in front of the volume discrepancy term (0.0 = off)  &  0.0d0 \\
\verb=  drdxfac =  & ratio of radial base state zones to Cartesian full state zones for spherical geometry  &  1 \\

@@

\verb=  evolve_base_state =  & turn on (.true.) or off (.false.) basestate evolution  &  .true. \\

@@

\verb=  grav_const =  & the gravitational acceleration (cm~s$^{-2}$) for plane-parallel geometry  &  -1.5d10 \\

@@

\verb=  init_shrink =  & the multiplicative factor ($\le 1$) to reduce the initial timestep as computed by the various timestep estimators   &  1.0 \\
